%
% Preface
\chapter{Preface}
This thesis came into existence after a long wander to search for a topic which suits my vision. I have always wanted to start my own robotics company some day. So the first thing that I decided was that my master thesis should have a strong practical work. To meet this goal, I set up an appointment with Subbu in his office where he explained to me about the topics which were available at the \ac {DCSC} robotics lab. At first, my topic was going to be "\ac {RL} for underactuated robot". Sounds novel and interesting. However, in terms of feasibility, this topic might become hard since there is only one underactuated robot in the lab, the slacklining robot, and it was not in a ready-to-program state. This means that I would have to spend much time making sure the robot work before I can apply my controller. Prof. Babu\v{s}ka then offers me a slightly similar topic but with totally different test bed. This is when I came into \ac {RL} for tracking control. This is a quite new topic in control field since only few people have conducted researches on it. After an hour of discussion, it is decided that this will be my thesis topic. The topic offers both theoretical and practical aspects since I will get a chance to apply my solution to a real robotic setup, UR5 from Universal Robots. Now that I am finishing my literature survey, I hope that I would deliver a satisfying result at the end of the thesis.

\vspace{30mm}
Delft, University of Technology \hfill \mscname \\
\mscdate